DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-12 Examples/Documentation/examples.tex
Section 4.2 in the docu: How to run existing examples

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How to run existing examples}
The easiest way is to first build all examples. Go into 
\begin{lstlisting}
dopelib/Examples/
\end{lstlisting}
Herein, type 
\begin{lstlisting}
make c-all
\end{lstlisting}
By typing only `make' you will see all options.
This procedure will take some minutes. Afterwards,
go into the examples folder of your choice. For instance:
\begin{lstlisting}
dopelib/Examples/PDE/InstatPDE/Example1
\end{lstlisting}
Herein you create the executable via
\begin{lstlisting}
make 
\end{lstlisting}
and then 
\begin{lstlisting}
./DOpE-PDE-InstatPDE-Example1 
\end{lstlisting}
Or both commands together:
\begin{lstlisting}
make && ./DOpE-PDE-InstatPDE-Example1 
\end{lstlisting}
You will find the results on the screen in the terminal as well
as some graphical output in the `Results' folder.
